Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-18 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued} Updating..

\subsection{From Real-valued to Interval-valued I}

@@

\begin{lemma}Consider an additive interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
Then, there is a quantum IVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that $\mathrm{core}\left(\bar{\mu}\right)$ has an unique element.
Obviously, if $\iota$ is convex, so does $\bar{\mu}$.\end{lemma}

\begin{proof}Consider $\bar{\mu}\left(P\right)=\iota\left(\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\left(P\right)\right)$.
Then, $\bar{\mu}\left(\proj{0}\right)=\iota\left(\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\left(\proj{0}\right)\right)=\iota\left(1\right)=\left[1,1\right]$,
i.e., for any quantum probability measure~$\mu\in\mathrm{core}\left(\bar{\mu}\right)$,
we have $\mu\left(\proj{0}\right)=1$. Therefore, $\mu=\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$.\end{proof}

@@

\subsection{From Real-valued to Interval-valued II}

>>>>

\subsection{From Real-valued to Interval-valued}

@@

\begin{lemma}Consider a set of intervals\nb$\mathscr{I}$ with an
additive interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
For any normalized pure state\nb$\ket{\phi}$, $\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}$
is a quantum IVPM such that $\mathrm{core}\left(\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}\right)$
has an unique element. Obviously, if $\iota$ is convex, so does $\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}$.\end{lemma}

\begin{proof}$\left(\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}\right)\left(\proj{\phi}\right)=\iota\left(\mu_{\phi}^{\mathrm{\mathrm{B}}}\left(\proj{\phi}\right)\right)=\iota\left(1\right)=\left[1,1\right]$,
i.e., for any quantum probability measure~$\mu\in\mathrm{core}\left(\iota\circ\mu_{\phi}^{\mathrm{\mathrm{B}}}\right)$,
we have $\mu\left(\proj{\phi}\right)=1$. Therefore, $\mu=\mu_{\phi}^{\mathrm{\mathrm{B}}}$.\end{proof}

@@

\subsubsection{Convex and Finite Number of Intervals in Low Dimension}

\subsubsection{Convex but Infinite Number of Intervals}
